a and generators

### 2022-03-31 documentos/intro.tex
intro outline almost finished

\par
In this work we present a generalization of Pauli channels that are also idempotent, \ie{} the qubit flip operations (bit, phase and bit-phase), total depolarizing qubit channel and the identity channel. It is known that not every linear operation mapping density matrices into density matrices is a valid quantum operation
[Role of completely positivity]
%
\par
The paper is organized as follows, in section~\ref{sec:pce_maps} we give a refreshing of quantum channels theory and the definition of \textit{Pauli component erasing maps} (\pce{}), being the generalization of idempotent Pauli channels aforementioned. In section~\ref{sec:math} we derive the 
% }}}

>>>>

\par
In this work we present a generalization of Pauli channels that are also idempotent, \ie{} the qubit flip operations (bit, phase and bit-phase), total depolarizing qubit channel and the identity channel. It is known that not every linear operation mapping density matrices into density matrices is a valid quantum operation
[Role of completely positivity]
%
\par
The paper is organized as follows, in section~\ref{sec:pce_maps} we give a refreshing of quantum channels theory and the definition of \textit{Pauli component erasing maps} (\pce{}), being the generalization of idempotent Pauli channels aforementioned. In section~\ref{sec:math} we diagonalize analytically the Choi matrix for arbitrary \pce{} maps and characterize completely positive maps by interpreting \pce{} maps as discrete vector spaces. In section~\ref{sec:generators} we study generators of the semigroup structure of the set of \pce{} channels

To finish, we conclude in section~\ref{sec:conclusions}.
% }}}
